---
title: "2ndSetOfExercises_R"
author: "Sofia Kampaki"
date: "November 25, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Exercise 1
####Construct a 5 x 10 matrix A, for which every Aij=ij Hint: remember that operations are cellwise in R.

```{r eval=F}
mtx1<-matrix(1:5,nrow=5,ncol=10)
mtx1
mtx2<-matrix(1:10,nrow=5,ncol=10,byrow=T)
mtx2
A=mtx1^mtx2
A
```

#Exercise 2
####Construct a 10 x 10 matrix A, for which Aij=|i−j|. Then extract its diagonal Hint: remember that operations are cellwise in R.
```{r eval=F}
mtx12<-matrix(1:10,nrow=10,ncol=10)
mtx22<-matrix(1:10,nrow=10,ncol=10,byrow=T)
mtx12
mtx22
Α=abs(mtx12-mtx22)
A
diag(Α)
```

#Exercise 3
####Create a 10 x 10 matrix A, for which Aij=(i−1)∗10+j.Hint: this is the easiest, you should just try to understand how this matrix should look like.

```{r eval=F}
A=matrix(1:100, nrow=10, ncol=10,byrow=T)
A
```

#Exercise 4
####Consider the matrix of the previous exercise (3). Find a matrix B, for which Bij=2×Aij. Find a matrix C, for which Cij=i×j×Aij
```{r eval=F}
D2<-matrix(2,ncol=10,nrow=1)
B=D2%*%A
B
C=mtx12%*%mtx22%*%A
C
```

#Exercise 5
####Create a list of 10 elements. Each element is a vector Vi=i,i=1…10
```{r eval=F}
test<-c(1:10)
test
v<-rep(list(0),10)
v
tmpl<-lapply(v,function(x) x<-c(1:10))
tmpl
```



#Exercise 6
####Convert the previous list to a 10×10matrix A, by row.
```{r, eval=F}
A<-matrix(unlist(tmpl),nrow=10,ncol=10,byrow=T)
A
```

#Exercise 7
####The same like exercise 6, by column.
```{r eval=F}
A<-matrix(unlist(tmpl),nrow=10,ncol=10)
A
```